\Trill: Secure firewall-traversing networking

### 2012-12-14 6.858/paper/paper.tex
Implementation section

@@

\subsection{Plume server}

>>>>

Our implementation of \Trill has two major components: a client library for
connecting to peers, and a set of server implementations which handle the
secure, federated message routing.

\subsection{Plume servers}

We break the server-side workload into two separate servers.  The first of
these is the \Plume login server.  The login server bears the full
responsibility of authenticating clients.  Each domain (or each login server on
each domain) can determine its own method for deciding whether or not to
endorse any given client's claimed identity.  This behavior is unspecified by
\Trill; the login server can only endorse identities in its domain, but can
endorse them however it sees fit.

The actual process of ``logging in'' requires a client to send the login server
a X.509 certificate signing request (CSR).  The login server, if it so chooses,
can then endorse the client's identity by signing a cert and returning it to
the user.  The client uses cert whenever it connects to \Plume protocol servers
or to peers in order to assert its identity.  These servers and parties can
then walk their way up the chain of trust to verify the user's identity and the
authority of the login server that endorsed it.

With this cert, the client is then able to connect to the \Plume protocol
servers.  These servers will only talk over TLS to clients with valid
identities (connections to the login servers are also secured by TLS, but only
the login server's cert is used).  These \Plume servers server two major
purposes:

\begin{enumerate}
  \item Message routing.  Clients can ask their \Plume servers to pass messages
    to peers.  If they are on the same domain and are connected to the server,
    the message is routed directly; otherwise, the message is forwarded first
    to the proper server
\end{enumerate}

Discovery of server addresses and ports

@@
